### 2023-06-12 paper/main.tex
figs_added

The result of antialiasing filtering is depicted in Figure \ref{Fig:symm_antialiasing} for the synthesis scenario discussed in the foregoing.
Figure (a) shows the result of the synthesis, while Figure (b) illustrates the spectrum of the bandlimited, sampled driving functions.
\begin{figure}[h!]
    \begin{center}
    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis.png}
        \footnotesize \put(0,2){(a)}
    \end{overpic} 
    \\
    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_spectrum.png}
        \footnotesize \put(0,0){(b)}
    \end{overpic}
\end{center}
    \caption{Symmetric antialiasing filtering}
\label{Fig:symm_antialiasing}
\end{figure}
It is highlighted, that

@@

\begin{figure}[h!]
    \begin{center}
    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_steered.png}
        \footnotesize \put(0,2){(a)}
    \end{overpic} 
    \\
    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_spectrum_steered.png}
        \footnotesize \put(0,0){(b)}
    \end{overpic}
\end{center}
    \caption{Non-symmetric antialiasing filtering}
\label{Fig:symm_antialiasing}
\end{figure}
\section*{Acknowledgment}

>>>>

The result of antialiasing filtering is depicted in Figure \ref{Fig:symm_antialiasing} for the synthesis scenario discussed in the foregoing.
Figure (a) shows the result of the synthesis, while Figure (b) illustrates the spectrum of the bandlimited, sampled driving functions.
\begin{figure}[h!]
    \begin{center}
    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis.png}
        \footnotesize \put(0,2){(a)}
    \end{overpic} 
    \\
    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_spectrum.png}
        \footnotesize \put(0,0){(b)}
    \end{overpic}
\end{center}
    \caption{Symmetric antialiasing filtering}
\label{Fig:symm_antialiasing}
\end{figure}
It is highlighted, that the presented antialiasing strategy ensures highly suppressed aliasing waves in the center of the circular source array.
In other positions of the listening area lateral aliasing wavefronts remain in the reproduced wave field, while the target, virtual wave front is bandlimited.
This phenomena can be easily understood by investigating the synthesis scenario in a geometrical manner:

From \eqref{eq:cutoff_fr} it is clear that since the antialiasing filter cutoff frequency is proportional with the tangential component of the virtual field on the SSD, therefore, in a circualr array a single SSD element will have nearly fullband driving signal: that SSD element at which the wavefront arrives perpendicularly.
This fullband SSD element is marked with white dot in Figure \ref{Fig:symm_antialiasing} (a).
From general WFS theory it is known that the fullband SSD element will dominate the synthesized wavefront (i.e. will serve as a stationary SSD position) for spatial positions along a straight line crossing through the actual SSD element into the direction of the local propagation vector.
Therefore, the present antialiasing strategy ensures aliasing-free synthesis along a straight line for which the fullband SSD element is the stationary secondary source. 
The direction of the line of aliasing-free synthesis is marked with a dashed arrow in the figure.
This is in contrast with conventional Local WFS approaches, in which the synthesis is optimized in the proximity of a pre-defined reference position over a circular area.

@@

\begin{figure}[h!]
    \begin{center}
    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_steered.png}
        \footnotesize \put(0,2){(a)}
    \end{overpic} 
    \\
    \begin{overpic}[width = 0.75\columnwidth]{figs/antialiased_synthesis_spectrum_steered.png}
        \footnotesize \put(0,0){(b)}
    \end{overpic}
\end{center}
    \caption{Non-symmetric antialiasing filtering}
\label{Fig:symm_antialiasing}
\end{figure}

It is important to emphasize that if no actual SSD element exists for a given plane wave direction (for which the wave arrives perpendicularly) then all the SSD elements are bandlimited, i.e.

\section*{Acknowledgment}
